Zaca Fire Type Conversion

### 2020-09-27 Model Data Sheets and Code/Manuscript_Code.Rmd
tried to run the manucript code. No go. it also takes FOREVER

library(tidyverse)
library(raster)
library(randomForest)
library(VSURF)
library(ALEplot)

@@

#Directory will all pre-processed Landsat images
setwd("E:/zaca/type_conversion/Imagery/Level2")

for(img in list.files(path = ".", "GTiff$")){

>>>>

library(tidyverse)
library(raster)
library(randomForest)
#library(VSURF)
library(ALEPlot)
library(tuneRanger)

@@

#Directory will all pre-processed Landsat images
setwd("E:/zaca/type_conversion/Imagery") #changed from: setwd("E:/zaca/type_conversion/Imagery/Level2")

for(img in list.files(path = ".", "tif$")){ # changed from for(img in list.files(path = ".", "GTiff$"))
